### 2025-07-23 machine-learning.qmd
20250723 - fix -- don't want to have to escape underscore b/c may not render in HTML/ePub

We use the optimal parameters identified during tuning.
We use a low learning rate (0.1) to avoid [overfitting](#sec-overfitting).
We set some light regularization (`lambda_l2`) for better generalization.
We also set the maximum tree depth (`max_depth`) at 5 to capture complex (up to 5-way) interactions, and set the maximum number of terminal nodes (`num_leaves`) per tree at $2^6$ (64)—though the number will not reach greater than $2^{\text{max_depth}} = 2^5 = 32$.
We set the minimum number of samples in any leaf (`min_data_in_leaf`) to be 100.

>>>>

We use the optimal parameters identified during tuning.
We use a low learning rate (0.1) to avoid [overfitting](#sec-overfitting).
We set some light regularization (`lambda_l2`) for better generalization.
We also set the maximum tree depth (`max_depth`) at 5 to capture complex (up to 5-way) interactions, and set the maximum number of terminal nodes (`num_leaves`) per tree at $2^6$ (64)—though the number will not reach greater than $2^{\text{max depth}} = 2^5 = 32$.
We set the minimum number of samples in any leaf (`min_data_in_leaf`) to be 100.
